ASTR480 Final Report:\\ \textit{Asteroids in TESS}

### 2024-10-05 FinalReport/FinalReportDraft.tex
some more

where the flux, $F$, is given in terms of time, $t$, the calculated frequency, f, and the model parameter $\vec{\theta} = [\theta_0, \theta_1,\theta_2]$.
These parameters are useful in reconstructing the sinusoid without rerunning the periodogram.
The method used for the periodogram fits is the new \texttt{nifty-ls} package \citep{Garrison2024} that has can be implemented on its own, or by interfacing with \texttt{Astropy}.
I use the later implementation as the speed up from the nonuniform fast Fourier transform is helpful on the large dataset from \texttt{TESSELLATE}, but the astropy interface is how I had everything set up to run on just one cut.

I an using a frequency window of for the periodogram between the the inverse of twice the time the asteroid spends in the sector and the Nyquist frequency (1/TESS cadance).

@@

The number of asteroids belong to each class of objects is highlighted in \autoref{Fig:NumPerClass}. As expected from the orbital elements in \autoref{Fig:AEI}, the majority of the minor planets fall in the three regions of the main belt. \dots

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{../OzData/classesBar29.pdf}
  \caption[Class distribution]{A distribution of the number of asteroids per class that \texttt{SkyBot} found in the Sector. 
  As with \autoref{Fig:AEI}, this is for all objects brighter than \nth{20}\unit{\mag}
  For the class labels, MB is ``main belt'' and ``NEA'' is near earth asteroid.}
  \label{Fig:NumPerClass}
\end{figure}

>>>>

where the flux, $F$, is given in terms of time, $t$, the calculated frequency, f, and the model parameter $\vec{\theta} = [\theta_0, \theta_1,\theta_2]$.
These parameters are useful in reconstructing the sinusoid without rerunning the periodogram.
The method used for the periodogram fits is the new \texttt{nifty-ls} package \citep{Garrison2024} that has can be implemented on its own, or by interfacing with \texttt{Astropy}.
I use the later implementation as the speed-up from the non-uniform fast Fourier transform is helpful on the large dataset from \texttt{TESSELLATE}, but the \texttt{Astropy} interface is how I had everything set up to run on just the subsection I was trialling my code on.

I am using a frequency window of for the periodogram between inverse of twice the time the asteroid spends in the sector and the Nyquist frequency (1/TESS cadence).

@@

The number of asteroids belonging to each class of objects is highlighted in \autoref{Fig:NumPerClass}. As expected from the orbital elements in \autoref{Fig:AEI}, the majority of the minor planets fall in the three regions of the main belt. 
There are some objects that are not asteroids, 20 comets were in the field and 1 centaur.
While they have a V mag less than 20, these objects are often not bright enough to have lightcurves with high enough mean fluxes to be detected well by TESS.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{../OzData/classesBar29.pdf}
  \caption[Class distribution]{A distribution of the number of objects per class that \texttt{SkyBot} found in the Sector. 
  As with \autoref{Fig:AEI}, this is for all objects brighter than \nth{20}\unit{\mag}
  For the class labels, MB is ``main belt'' and ``NEA'' is near earth asteroid.}
  \label{Fig:NumPerClass}
\end{figure}
